\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-09 report/article_4.tex
bringing web writeup inline with report

The rankings used in Figure 3 made use of the $drift$ parameter of
ARIMA models, combined with statistical volatility over the five year
house prices dataset. Both parameters were converted to quantiles and
weighted equally, with those sectors with the largest projected growth
and lowest historical volatility receive the highest investment grade.\textsuperscript{$\star$}

@@

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
%\clearpage
\section*{Value generation}

The above-described analyses form the basis of \logo\hspace{.1em}, a
start-up aimed at ``democratising real estate investment'' by
making deep-dive analytics data available both to a consumer and
professional investment market.

@@

\begin{wrapfigure}[11]{r}{.4\textwidth}
\centering
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
\vspace{-2em}
\end{wrapfigure}

@@

Having established a property area analytics brand, \logo\hspace{.1em}
will look to develop business relationships with real estate
investment funds and high net-worth individuals as a data-driven
propert investment consultancy and independent analyst for the
financial services. Our domain expertise and existing partnerships and
products would place us as a market leader in this undeveloped segment.

@@

\vspace{1em}
\begin{flushright}
{\small An enhanced overview of this entry is available online at: \leavevmode\href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}

>>>>

The rankings used in Figure 3 made use of the $drift$ parameter of
ARIMA models, combined with statistical volatility over the five year
house prices dataset. Both parameters were converted to quantiles and
weighted equally; those sectors with the highest projected growth
and least historical volatility receive the highest investment grade
(on a scale of AAA, AA, A, BBB \ldots C).\textsuperscript{$\star$}

Returning to our original example, we can conclude that SW18 4HU is a
promising choice of area for property investment. It's approximately
median-priced for the sector, which is the cheapest of SW18 (in turn
part of the desirable SW London area; Figure 1). It has good growth
projections of XX in the next 12 months (Figure 2), and when combined
with volatility and compared with all $\approx2600$ sectors in the
dataset, receives the top AAA investment grade, placing it in the
90\textsuperscript{th} percentile for predicted price growth and low
historical volatility.

@@

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
\clearpage
\section*{Value generation}

The above-described analyses form the basis of \logo\hspace{.1em}, a
start-up aimed at ``democratising real estate investment'' by making
deep-dive analytics data available both to a consumer and professional
investment market. Initially \logo\hspace{.1em} is a provider of
information aimed at investors but cannot dispense investment advice
until authorised to do so by the FCA. Three initial areas of interest
to commercialise and generate social and economic value are listed:

@@

\begin{wrapfigure}[12]{r}{.4\textwidth}
\centering
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
%\vspace{-1em}
\end{wrapfigure}

Releasing these products aligns with our aims of democratising real
estate investment. Amateur property investors and prospective
landlords can make data-driven decisions, the likes of which are likely
already employed by large investment trusts and funds.

@@

Having established a property area analytics brand, \logo\hspace{.1em}
will look to develop business relationships with real estate
investment funds and high net-worth individuals as a {\bf quantitative
  property investment consultancy} and independent analyst for the
financial services. Our domain expertise and existing partnerships and
products would place us as a market leader in this undeveloped
segment.

@@

\vspace{1em}
\begin{flushright} {\small An enhanced online version of this short
    report is available at:
    \leavevmode\href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}
